\documentclass[letterpaper,10.5pt]{article}
\usepackage[margin=0.6in, top=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{multicol}

\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black
}

\titleformat{\section}{\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{4pt}

\setlength{\parindent}{0pt}
\pagestyle{empty}

\begin{document}

% ──────────────────────────────────────────────
%  HEADER
% ──────────────────────────────────────────────
\begin{center}
  {\LARGE \textbf{Jack Oien}} \\[4pt]
  \href{mailto:oiendjack@gmail.com}{oiendjack@gmail.com} \;|\;
  612-757-8523 \;|\;
  Duluth, MN \\[2pt]
  \href{https://github.com/r-b-1}{github.com/r-b-1} \;|\;
  \href{https://linkedin.com/in/jack-oien-93aa43369}{linkedin.com/in/jack-oien-93aa43369} \;|\;
  \href{https://r-b-1.github.io/wad}{r-b-1.github.io/wad}
\end{center}

% ──────────────────────────────────────────────
%  EDUCATION
% ──────────────────────────────────────────────
\section{Education}

\textbf{University of Minnesota Duluth} \hfill Expected May 2027 \\
B.S. Computer Science \\
\textit{Relevant Coursework:} Data Structures, Software Engineering,
Computer Architecture, Computer Security, Software Design

% ──────────────────────────────────────────────
%  WORK EXPERIENCE
% ──────────────────────────────────────────────
\section{Work Experience}

\textbf{Planet Fitness} \hfill September 2024 -- Present \\
\textit{Team Lead, Front Desk}
\begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=3pt]
  \item Led front desk operations and assisted in onboarding and
        training new team members.
  \item Managed member accounts including membership creation,
        cancellation, billing updates, and personal information changes.
  \item Handled high-volume customer inquiries and resolved complaints
        in a fast-paced environment.
\end{itemize}

\textbf{Great Lakes Roofing and Siding} \hfill July 2025 -- Present \\
\textit{Field \& Office Assistant}
\begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=3pt]
  \item Automated customer outreach using a Google Sheets extension,
        sending 15 follow-up emails per week and recovering the
        company's review count from 0 to 32 across 107 total reviews.
  \item Transported materials to and from job sites, prepared
        worksites before crews arrived, and handled post-job cleanup.
\end{itemize}

% ──────────────────────────────────────────────
%  PROJECTS
% ──────────────────────────────────────────────
\section{Projects}

\textbf{AI Desktop Chat} \hfill
\textit{Tauri, Rust, React 19, TypeScript, Supabase, OpenAI} \hfill 2025 -- Present \\
\href{https://github.com/r-b-1}{github.com/r-b-1}
\begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=3pt]
  \item Built a native macOS desktop app in Tauri (Rust) + React 19
        that monitors any on-screen window, runs OCR via the macOS
        Vision framework, detects question patterns, and dispatches
        them to GPT-4o mini in under a second.
  \item Implemented perceptual hashing (pHash) on a 400 ms Tokio
        background loop to skip unchanged frames, keeping CPU usage
        low during continuous watch sessions.
  \item Engineered streaming OpenAI responses over SSE with
        exponential backoff + jitter retry (429/5xx), and live web
        search with per-message inline URL citations.
  \item Integrated Supabase for user authentication and persisted
        multi-session chat history (PostgreSQL + Storage) with full
        create, rename, and delete support.
\end{itemize}

\vspace{4pt}

\textbf{Bloc Party} \hfill
\textit{Flutter, Dart, Firebase, Google Maps API} \hfill Fall 2025 \\
\href{https://github.com/r-b-1/bloc-party}{github.com/r-b-1/bloc-party}
\begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=3pt]
  \item Owned the home screen and item data layer in a 5-person team
        — built the Firestore item model, live item feed,
        neighborhood-scoped filtering, search/filter widget, and
        asset image system with fallback error handling.
  \item Built a JSON-driven runtime theme system using Provider,
        enabling light/dark/custom themes switchable without app
        restart.
  \item Implemented public/private item description views scoped by
        ownership and integrated with the borrow scheduling flow.
\end{itemize}

\vspace{4pt}

\textbf{Zork-Style Adventure Engine} \hfill
\textit{C++} \hfill Fall 2023 \\
\begin{itemize}[leftmargin=1.5em, itemsep=1pt, topsep=3pt]
  \item Reverse-engineered Zork's terminal mechanics and designed an
        original world with branching narrative in C++, with a
        5-person team using Git and UML class diagrams.
  \item Established documentation standards and introduced structured
        Git workflow for the team's first collaborative project.
\end{itemize}

% ──────────────────────────────────────────────
%  SKILLS
% ──────────────────────────────────────────────
\section{Skills}

\textbf{Languages:} Dart, TypeScript, Rust, Python, Java, C++ \\
\textbf{Frameworks \& Tools:} Flutter, React, Tauri, Vite, Firebase,
Supabase, OpenAI API, Google Maps API \\
\textbf{Concepts:} REST APIs, SSE Streaming, OCR, OOP, Git,
MVC Architecture, Agile/Scrum

\end{document}
